% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

What is the measure of a man? A woman? A marriage?\\
Is there a ruler? Is there a scale? How do you reckon it?\\
Is 10 a lot? A little? Depends on 10 what? Right?\\
10 ants crawling on the back lanai is better than a 1,000.\\
10 grams of gold is valued today at \$577.12.

It was in my life's ancient of days that I knew\\
that length of days is no way to judge\\
the quality of a person's life.\\
Dale Evans' \emph{Angel Unaware.} You know the story.\\
We've had 10 years to share stories.

Is that a lot? Is 10 times that 10 times better?\\
Is knowing you and your stories quantifiable?\\
Is taking you for my \textbf{isha} ``no matter what''\\
a thing to be measured?\\
``All Welcomed. All Loved. No Exceptions.''\\
reads the motto on the church we chose.\\
That's tough to incarnate.\\
10 years is 10 years of enfleshing ``I love you'' -no matter what.\\
That's something, not to be sneezed at, no laughing matter.

You asked once if there was \textbf{chemistry}?\\
Oh, indeed.\\
No matter what, no exceptions -it's easier today,\\
I'm more assured, than yesterday -multiplied back\\
10 years.

I remember the evening by the jewelry shop along the north shore\\
When I asked you to marry me. I remember it again and again.\\
\emph{Anamnesis} remembers into being, a sacrament,\\
A presence in time present, time past and yet to come.

10 years is long enough to know many of your stories.\\
Not really long enough to hear a year's worth of\\
retelling the story in a new year's new context.\\
It's long enough to see you in the morning,\\
looking like a song rising from the mist off a forested lake.\\
And a smile rises up within me.

10 years is long enough to have traveled together thousands of miles,\\
But there are still miles and miles that lie before us.\\
Take your pick. I would still choose you. Today I delight inside when I
look up at you And I see a beautiful woman. It's not words. It's what I
see. I may be crazy. But I'm in love with you at the mile-marker 10
years.

\end{document}
